A statistical analysis of a counterstrike game: Boston 2018

### 2025-03-06 inst/counterstrike.Rmd
more work

@@

@@

```{r calcklikef, cache=TRUE}
f <- function(l){maxp(mk(l), give=1)$`Log-likelihood`}
lam <- seq(from = 0.01,to = 1.1, len = 43)
L <- sapply(lam, f)
```

```{r plotlikelam}
plot(lam, L - max(L), type='b')
plot(log(lam), L - max(L), type='b')
```

```{r}
maxp(mk(optlam$maximum))
```

>>>>

```{r, counterh2, echo=TRUE}
H <- hyper2()
  for(i in seq_len(nrow(a))){
      d <- strsplit(a$deathorder[i],", ")[[1]]
      H <- H + suppfun(d)
  }
H
samep.test(H,c("Skadoodle","Stewie2K"))
```

@@

Find the MLE for $\lambda$:

And the BT strengths at the evaluate:

```{r BTatevaluate, cache=TRUE}
maxp(mk(optlam$maximum))
```

@@

```{r calcklikelam, cache=TRUE}
f <- function(l){maxp(mk(l), give=1)$`Log-likelihood`}
lam <- exp(seq(from = -4,to = log(1.1), len = 33))
L <- sapply(lam, f)
```

```{r findinterval, cache=TRUE}
g <- function(l){f(l) - optlam$objective  + 2}
jj1 <- uniroot(g, interval = exp(c(-4,-3)))
jj2 <- uniroot(g, interval = exp(c(-1,-0)))
jj1
jj2
```

```{r plotlikelam}
plot(log(lam), L - max(L), type='l')
segments(x0=log(optlam$maximum),y0 = -0.5, y1 = 0.1,col='red')
abline(h=c(0,-2), col = 'gray')
segments(x0 = log(jj1$root), y0 = -2.2, y1 = -1.8, col = 'blue')
segments(x0 = log(jj2$root), y0 = -2.2, y1 = -1.8, col = 'blue')
abline(v = 0, lty = 2)
```
